Rectangulotopes

### 2024-04-04 draft/rectangulotopes.tex
Section 4.4

\begin{lemma}
  The strong rectangulotope $\SRP(n)$ is realized by the following submodular function:
  \[
  f(S) \eqdef \# \bigset{ I, J }{ I\cap S\not=\emptyset \wedge J\cap ([n]\ssm S) \not= \emptyset } +
  \#\bigset{ I, J }{ J\cap S\not=\emptyset \wedge I\cap ([n]\ssm S) \not= \emptyset },
  \]
  where $I, J$ are pairs of consecutive and nonempty intervals of $[n]$.
\end{lemma}

\begin{proof}
  From \cref{lem:strongMinkowski,lem:submodsum}, the submodular function defining the realization of $\WRP(n)$ is the sum of the submodular functions defining the yin and yang shard polytope in \cref{lem:yinsp,lem:yangsp}. For a yin arc $A$ defined by consecutive intervals $I, J$ of $[n]$, we have that its shard polytope $\SP(A)$ is realized by the submodular function
  \[
  \yin{f}_{I,J}(S) \eqdef \llbracket S\cap I\not=\emptyset \wedge S\not\supseteq J \rrbracket .
  \]
  Similarly, for a yang arc, the shard polytope $\SP(A)$ is defined by the following submodular function:
  \[
  \yang{f}_{I,J}(S) \eqdef \llbracket S\cap J\not=\emptyset \wedge S\not\supseteq I \rrbracket .
  \]
  Their sum
  \[
  f(S) \eqdef \sum_{I,J} \yin{f}_{I,J}(S) + \yang{f}_{I,J}(S)
  \]
  is therefore as claimed.
\end{proof}

>>>>

\begin{lemma}
  The strong rectangulotope $\SRP(n)$ is realized by the following submodular function:
  \[
  f(S) \eqdef \# \bigset{ I, J }{ I \not\subseteq [n] \ssm S \text{ and } J \not\subseteq S } +
  \#\bigset{ I, J }{ I \not\subseteq S \text{ and } J \not\subseteq [n] \ssm S },
  \]
  where $I, J$ are pairs of nonempty consecutive intervals of~$[n]$.
\end{lemma}

\begin{proof}
  The submodular function defining the realization of $\WRP(n)$ is the sum of the submodular functions defining the yin and yang shard polytopes in \cref{lem:yinsp,lem:yangsp}.
  The shard polytope~$\SP(\yinArc{I}{J})$ of a yin arc $\yinArc{I}{J}$ is given by the submodular function
  \[
  f_{\yinArc{I}{J}}(S) \eqdef \llbracket I \not\subseteq [n] \ssm S \text{ and } J \not\subseteq S \rrbracket .
  \]
  (Recall that $\llbracket \varphi\rrbracket$ is equal to 1 if $\varphi$ holds, and 0 otherwise.)
  Similarly, the shard polytope~$\SP(\yangArc{I}{J})$ of a yang arc~$\yangArc{I}{J}$ is given by the submodular function
  \[
  f_{\yangArc{I}{J}}(S) \eqdef \llbracket I \not\subseteq S \text{ and } J \not\subseteq [n] \ssm S \rrbracket .
  \]
  Their sum
  \[
  f_{\strongeq}(S) \eqdef \sum_{I,J} f_{\yinArc{I}{J}}(S) + f_{\yangArc{I}{J}}(S)
  \]
  is therefore as claimed.
\end{proof}
